\chapter{Future Work}
\textit{This section I will discuss future work of research few areas, like wearable sensors, chatbot integration}
\vspace{5mm}

As with every research, some ends need further research and in our case a few ends that also
needs further research is the implementation.

Stress cannot be directly measured but it can be determined by certain characteristics in primary measures. The primary measures were considered in isolation or in some fundamental combination. Appropriately collected and collated physiological and physical signals can be used for stress measurement, which requires consideration of multi-source alignment. Future work could involve researching and modelling latency's for physiological and physical signals to the fusion of primary stress measurement measures and using techniques such as dynamic time warping to find optimal alignment.

Chatbots may be used to transform diagnostic scales into a more user-friendly way to screen for mental health issues. Most validated screening devices are typically administered in a paper-based format before counselling. Online versions of these screening tools are available but it can be laborious to fill in for the user. This could potentially deter the user from responding correctly to the questions.

Conversation flow for an interactive chatbot that converses with users who experience workplace stress. If the user indicates they feel fine, randomized tips on general well-being will be given and the option of exiting or restarting the chatbot will be given. 

Another pathway, for general difficulties not related to the workplace, will lead to a wide variety of issues from which the user can choose to receive more information and tips for self-help.

Another pathway will lead to a general stress program that a clinical psychologist has devised. For users who experience negative feelings directly from reviewing disturbing online content, a specific pathway has been created which leads to a screening tool based on the impacts of event scale for trauma assessment. This chatbot will be incorporated into a wider web application that will screen and support staff working in the workplace with troubling online media.