\begin{acknowledgements}

All praise, honor, and glory to my Lord Allah for the many blessings I have encountered, during the times at the university and especially in Bremen. Also, I cannot
forget to express my deepest gratitude to the messenger of my Lord and most
respectable personality, Prophet Mohammed (Peace Be Upon Him).

My sincere thanks to my thesis supervisor and reviewer Dr. Benjamin Tannert at the University
of Bremen to give me the opportunity to do my thesis under his supervision. Through
this opportunity, I was able to gain a lot of knowledge in this exciting field of research and for that I am grateful.

I would also like to acknowledge Prof. Dr. Heidi Schelhowe at the University of Bremen
as the second reviewer of this thesis, for the valuable comments and the guidance on this thesis work.

Many special thanks go to my co-supervisor Michael Lund, Research associate, FAB lab at University of Bremen for the support during this period, especially for the invested time, the topics about stress management for special needs people and having an eye on the challenge paper. 

Thanks a lot to Jan Brunkenhövers, for his helpful suggestions and supports during the work.

Finally, for all the support and patience, I would like to express my deepest gratitude to my father Amir Hamza, mother Hasina Begum and friends, especially, my wife Jannatul Ferdush Ridoy for supporting me far from more then 8000 km, that was there from the beginning and the ones I have found along the way, while doing the unexpected.
\end{acknowledgements}